Compositional Equivalences Based on Open pNets

### 2022-10-09 2016-Weak-FH-Bisim/JLAMP-AnswerToReviewers.tex

\documentclass[10pt]{article}
\usepackage[latin1]{inputenc} 
\usepackage{alltt,url}
%% Old ttbox definition without frame:
\newenvironment{ttbox}{\begin{alltt}\small\tt}%
                      {\end{alltt}}
\usepackage{color}
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
\thispagestyle{empty}
\addtolength{\textheight}{2cm}
\begin{document}
\section*{Answer to reviewers }
\subsection*{Submission to Journal of Logical and Algebraic Methods in Programming}
\medskip
\begin{ttbox}
Title: Compositional equivalences based on Open pNets
Authors: R. Ameur-Boulifa, L. Henrio, and E. Madelaine
\end{ttbox}
\bigskip
%\subsubsection*{Letter to Reviewers and Editors}
Dear reviewers and editors,

\ERIC{P4, *say that this is like in Symbolic Bisimulation
\begin{quote}Pas sur du tout, je bosse encore la-dessus...
\end{quote}}

\ERIC{P4, *Any relations with the conditions on SOS rule formats guaranteeing compositionality of weak bisimilarity?
\begin{quote} non je n'ai pas repondu ici... voir paragraph page precedente, est-ce suffisant "
\end{quote}}

\ERIC{P14, *Is your definition a combination of De Simone FH-bisimulation and Hennessy and Lin's symbolic bisimulation?
\begin{quote}
Je n'ai pas redige ca... mais l'idee pourrait etre que en gros oui, et en y ajoutant le formalisme synch vecteurs de Arnold et Nivat, 
mais que notre approache est sensiblement differente, puisque plus syntaxique, pour permettre le developpement de representation finies, d'algorithmes, et d'outils...
\ned{quote}

\ERIC{P17, *What is the comoplexity of this "brute force approach"?
\begin{quote}
le paragraph existant etait difficilement comprehensible et loin de notre implementation dans l'outil. J'ai remplace par quelque chose de plus factuel:
"The definition of this predicate is not constructive. In our tool [39], we construct a logical formula encoding the matching and unification conditions involved, and let an SMT engine (in the current implementation Z3 [30]) decide its satisfiability"
\end{quote}}

\ERIC{page 36, *It'd be a good idea to give links to software tools implementing your approach and to examples case-studies
\begin{quote}
J'ai ajoute 7 ligns ici: "In this platform [...] different encodings of operators".
C'est un peu faible parceque 1) les outils de sont pas encore accessibles en ligne (ca aurait du etre l'achevement du stage de Slava...), et 2) on n'a pas de papier sur un vrai "use-case', a part le AVOCS sur le satellite, mais qui ne fait pas de bisimulation, juste des proprietes temporelles.
\end{quote}}

\begin{flushright}
  Best Regards,\\
  Rab\'ea Ameur-Boulifa, Ludovic Henrio, and Eric Madelaine
\end{flushright}
\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2022-10-10 2016-Weak-FH-Bisim/WeakBisim.tex
papier Larsen
statechart

Each sub-pNet exposes
a set of actions, called \emph{internal actions}. The synchronisation between global actions exposed by the pNet and
internal actions of its sub-pNets is given by  \emph{synchronisation vectors}: a
synchronisation vector synchronises one or several internal actions, and
exposes a single resulting global action.

We now define the structure of pNets, the following definition relies on the definition 
of holes, leaves and sorts formalised below in Definition~\ref{def-sortholeleave}. Informally, holes are process parameters, leaves provide the set of pLTSs at the leaves of the hierarchical structure of a pNet, and sorts give the signature of a pNet, i.e. the actions it exposes.
\TODO{Rabea: look for papers by Larsen end Liu on context systems, and Larsen and Huttel on static constructs}

@@

Methodologies for reasoning about abstract semantics of open systems can be found in \cite{BaldanBB:2002, BaldanBB:07,Dubut:20}, authors introduce  behavioural equivalences for open systems from various symbolic approaches. Working in the setting of process calculi, some close relations  exist with the work  of the authors of \cite{BaldanBB:2002,BaldanBB:07}, where both approaches are based
on some kinds of labelled transition systems. The distinguishing feature of their approach is that the transitions systems are labelled with logical formulae that provides  an abstract characterization of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire. Logical formulae are suitable formalisms that capture the general class of components that can act as the placeholders of the system during its evolution. In our approach we purposely leave the algebra of action terms undefined but the only operation we allow on action of holes is the comparison with other actions. Defining properly the interaction between a logical formulae in the action and the logics of the pNet composition seems very difficult.
\TODO{Rabea: look for "quotienting techniques"}

>>>>

Each sub-pNet exposes
a set of actions, called \emph{internal actions}. The synchronisation between global actions exposed by the pNet and
internal actions of its sub-pNets is given by  \emph{synchronisation vectors}: a
synchronisation vector synchronises one or several internal actions, and
exposes a single resulting global action.
\RAB{Pas sur au bon endroit mais -- The pNets model is hierarchical in the structure of the processes, in contrast to the Statecharts formalism \cite{Harel:87}, which is widely used to model high-level behaviour,  that organises the states in a hierarchy.}

We now define the structure of pNets, the following definition relies on the definition 
of holes, leaves and sorts formalised below in Definition~\ref{def-sortholeleave}. Informally, holes are process parameters, leaves provide the set of pLTSs at the leaves of the hierarchical structure of a pNet, and sorts give the signature of a pNet, i.e. the actions it exposes.
\RAB{In the same vein as for context systems \cite{Larsen:91}, pNets is a formalism for modular and possibly incomplete  description of concurrent systems. The theory of contexts relies on a form of rewrite rules, while the pNets on the notion of automata.  }
\TODO{Rabea: look for papers by Larsen end Liu on context systems, and Larsen and Huttel on static constructs}

@@

Methodologies for reasoning about abstract semantics of open systems can be found in \cite{BaldanBB:2002, BaldanBB:07,Dubut:20}, authors introduce  behavioural equivalences for open systems from various symbolic approaches. Working in the setting of process calculi, some close relations  exist with the work  of the authors of \cite{BaldanBB:2002,BaldanBB:07}, where both approaches are based
on some kinds of labelled transition systems. The distinguishing feature of their approach is that the transitions systems are labelled with logical formulae that provides  an abstract characterization of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire. Logical formulae are suitable formalisms that capture the general class of components that can act as the placeholders of the system during its evolution. In our approach we purposely leave the algebra of action terms undefined but the only operation we allow on action of holes is the comparison with other actions. Defining properly the interaction between a logical formulae in the action and the logics of the pNet composition seems very difficult.
\RAB{This is despite the fact that our approach can support alternative techniques for overcoming the state-space-explosion problem  as quotienting technique for compositional model checking  \cite{Larsen:91}.} 
\TODO{Rabea: look for "quotienting techniques"}
